Recursive algorithms, branching coefficients and applications

### 2010-07-05 AffineLieAlgebras/InformalNotes/article.tex
pdf insured for pdflatex
Update to arXiv version
Compilation to dvi with eps images in IOP style is successful, paper size is 24 pages. Note that the renaming of figures is required.

\documentclass[a4paper,12pt]{article}
\usepackage{ucs}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{pb-diagram}
\usepackage{multicol}
%\usepackage[utf8x]{inputenc}
%\usepackage[russian]{babel}
\usepackage{cmap}
\usepackage{color}
%\usepackage[pdftex]{graphicx}
\usepackage{graphicx}
\pagestyle{plain}
\usepackage[unicode,verbose,plainpages=false]{hyperref}

%\usepackage{verbatim} 
\newenvironment{comment}
{\par\noindent{\bf TODO}\\}
{\\\hfill$\scriptstyle\blacksquare$\par}

\newtheorem{statement}{Statement}
\newtheorem{note}{Note}[section]
\theoremstyle{definition} \newtheorem{Def}{Definition}
\newcommand{\go}{\overset{\circ }{\frak{g}}}
\newcommand{\ao}{\overset{\circ }{\frak{a}}}
\newcommand{\co}[1]{\overset{\circ }{#1}}

\begin{document}
\pagenumbering{alph}
\thispagestyle{empty}

\begin{center}
{\Large \bf SAINT-PETERSBURG STATE\\[0.5cm] UNIVERSITY}
\end{center}
\vskip 1 cm
\begin{flushright}
{\large \bf SPbU-IP-10-03}
\end{flushright}
\hfill {}
\vskip 1 cm
\begin{center}
{\Huge \bf Recursive algorithms, branching coefficients \\ and applications\\[0.5cm]
}
\end{center}
\vskip 1.0 cm
\begin{center}
{\Large \bf
Vladimir Lyakhovsky\\[2mm]
Anton Nazarov}
\end{center}
\vfill
\begin{center}
{\large Department of Theoretical Physics\\
}
\end{center}
\vfill
\begin{center}
SAINT-PETERSBURG \\
2010
\end{center}

\newpage

\pagenumbering{arabic}
\title{\textbf{{\Large {Recursive algorithms, branching coefficients and applications}}}}
\author{Vladimir Lyakhovsky \thanks{ Supported by
 RFFI grant N 09-01-00504 and the National Project RNP.2.1.1./1575 }\\
Theoretical Department, SPb State University,\\
198904, Sankt-Petersburg, Russia \\
e-mail:lyakh1507@nm.ru \\
[5mm] Anton Nazarov \thanks{ Supported by
the National Project RNP.2.1.1./1575 }\\
Theoretical Department, SPb State University,\\
198904, Sankt-Petersburg, Russia \\
e-mail:antonnaz@gmail.com
}
%\maketitle

\begin{abstract}
  Recurrent relations for branching coefficients in affine Lie algebras integrable highest weight modules are studied. The decomposition algorithm based on the injection fan technique is adopted to the situation where the Weyl denominator becomes singular with respect to a reductive subalgebra. We study some modifications of the injection fan technique and demonstrate that it is possible to define the "subtracted fans" that play the role similar to the original ones. Possible applications of subtracted fans in CFT models are considered.
\end{abstract}

@@

$r$ , $\left( r_{\frak{a}}\right) $ --- the rank of the algebra $\frak{g}$ $%
\left( \text{resp. }\frak{a}\right) $ ;

$\Delta $ $\left( \Delta _{\frak{a}}\right) $--- the root system; $\Delta
^{+} $ $\left( \text{resp. }\Delta _{\frak{a}}^{+}\right) $--- the positive
root system (of $\frak{g}$ and $\frak{a}$ respectively);

@@

$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\frak{a}}^{\nu }\right) $ --- the
weight diagram of $L^{\mu }$ $\left( \text{resp. }L_{\frak{a}}^{\nu }\right)
$ ;

@@

$\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ --- the $i
$-th (resp. $j$-th) basic root for $\frak{g}$ $\left( \text{resp. }\frak{a}%
\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;

@@

$\alpha _{i}^{\vee }$ , $\left( \alpha _{\left( \frak{a}\right) j}^{\vee
}\right) $--- the basic coroot for $\frak{g}$ $\left( \text{resp. }\frak{a}%
\right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;

$\co{\xi }$ , $\co{\xi _{\left( \frak{a}\right) }}$
--- the finite (classical) part of the weight $\xi \in P$ , $\left( \text{%
resp. }\xi _{\left( \frak{a}\right) }\in P_{\frak{a}}\right) $;

@@

$P$ $\left( \text{resp. } P_{\frak{a}}\right) $ \ --- the weight lattice;

$M \left( \text{resp. }M_{\frak{a}}\right) :=$

\noindent $=\left\{
\begin{array}{c}
\sum_{i=1}^{r}\mathbf{Z}\alpha _{i}^{\vee }\text{ }\left( \text{resp. }%
\sum_{i=1}^{r}\mathbf{Z}\alpha _{\left( \frak{a}\right) i}^{\vee }\right)
\text{for untwisted algebras or }A_{2r}^{\left( 2\right) }, \\
\sum_{i=1}^{r}\mathbf{Z}\alpha _{i}\text{ }\left( \text{resp. }\sum_{i=1}^{r}%
\mathbf{Z}\alpha _{\left( \frak{a}\right) i}\right) \text{for }A_{r}^{\left(
u\geq 2\right) }\text{ and }A\neq A_{2r}^{\left( 2\right) },
\end{array}
\right\} ;$\\
$\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w\circ (\mu +\rho )-\rho }$ --- the singular weight element for the $\frak{g}$-module $L^{\mu }$;
$\Psi _{\left( \frak{a}\right) }^{\left( \nu \right) }:=\sum\limits_{w\in W_{\frak{a}}}\epsilon (w)e^{w\circ (\nu +\rho
_{_{\frak{a}}})-\rho _{_{\frak{a}}}}$ --- the corresponding singular weight
element for the $\frak{a}$-module $L_{\frak{a}}^{\nu }$;

$\widehat{\Psi ^{\left( \mu \right) }}$ $\left( \widehat{\Psi _{\left( \frak{%
a}\right) }^{\left( \nu \right) }}\right) $ --- the set of singular weights $%
\xi \in P$ $\left( \text{resp. }\in P_{\frak{a}}\right) $ for the module $%
L^{\mu }$ $\left( \text{resp. }L_{\frak{a}}^{\nu }\right) $ with the
coordinates $\left( \co{\xi },k,n,\epsilon \left( w\left( \xi
\right) \right) \right) \mid _{\xi =w\left( \xi \right) \circ (\mu +\rho
)-\rho },$ (resp. $\left( \co{\xi },k,n,\epsilon \left(
w_{a}\left( \xi \right) \right) \right) \mid _{\xi =w_{a}\left( \xi \right)
\circ (\nu +\rho _{a})-\rho _{a}}$ ),

$m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\xi }^{\left( \nu \right)
}\right) $ --- the multiplicity of the weight $\xi \in P$ \ $\left( \text{%
resp. }\in P_{\frak{a}}\right) $ in the module $L^{\mu }$ , (resp. $\xi \in
L_{\frak{a}}^{\nu } $);

$ch\left( L^{\mu }\right) $ $\left( \text{resp. }ch\left( L_{\frak{a}}^{\nu
}\right) \right) $--- the formal character of $L^{\mu }$ $\left( \text{resp. }%
L_{\frak{a}}^{\nu }\right) $;

@@

\noindent $\left( \text{resp. }R_{\frak{a}}:=\prod_{\alpha \in \Delta _{%
\frak{a}}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\frak{a}}\mathrm{%
\left( \alpha \right) }}=\Psi _{\frak{a}}^{\left( 0\right) }\right) $--- the
denominator.

@@

Our aim is to demonstrate that despite the zeros arriving in the Weyl denominator $R$
(when it is projected to the $P_{\mathfrak{a}}$) the injection fan technique \cite{ilyin812pbc} can be properly modified.
The result is the generalized recurrent relation for anomalous branching
coefficients \eqref{eq:21}:
\begin{equation}
  \label{eq:1}
  \begin{array}{c}
      k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+ \right.\\
\left.
+\sum_{\gamma \in
\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
+\gamma }^{\left( \mu \right) }\right)
  \end{array}
   \end{equation}
Here $\mathfrak{a}_{\bot}$ is the subalgebra fixed by those roots of $\mathfrak{g}$ that are
orthogonal $P_{\mathfrak{a}}$, $W_{\bot}$ is the corresponding Weyl group,
$\Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ is the set of weights in the expansion
of the product $\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\mathfrak{a}_{\bot}}}
(1-e^{-\alpha})^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\alpha)}$ and $s(\gamma)$
is the multiplicity of $e^{\gamma}$ in this expansion.
In the next subsection we study the situation in details and prove the relation \eqref{eq:1}.

@@

Such effects are due to the fact that the subalgebras $\mathfrak{a}$ and $\mathfrak{a}_{\bot}$ must not form a direct sum in $\mathfrak{g}$.  
Consider the case of such a regular embedding $\mathfrak{a}\subset \mathfrak{g}$ where both algebras are simple and the diagram of the subalgebra $\mathfrak{a}_{\bot}$ is not a subdiagram of the extended Dynkin diagram $\mathfrak{g}$.
 Drop the subdiagram of $\mathfrak{a}$ and the node $\alpha'$ that connects it with all the remaining nodes of the diagram of $\mathfrak{g}$. The remaining diagram is the diagram of the algebra $\mathfrak{\bar{a}}$ with $\mathrm{rank}(\mathfrak{\bar{a}}) = \mathrm{rank}(\mathfrak{g})-\mathrm{rank}(\mathfrak{a})$. It is clear that $\mathfrak{\bar{a}}\subset \mathfrak{a}_{\bot}$. So the question is whether $\mathfrak{a}_{\bot}$ has additional roots,  not the roots of $\mathfrak{\bar{a}}$ but the linear combinations of them. The answer is positive  when the set of angles between the roots of $\mathfrak{\bar{a}}$ does not contain all the angles between the roots of $\mathfrak{a}$. Then by reflecting the roots of $\mathfrak{a}$ by $s_{\alpha'}$ we get the additional roots of $\mathfrak{a}_{\bot}$. 
\begin{table}[ph]
\label{tab:diagrams}
\noindent  \centering{
\begin{tabular}{|l|l|l|l|}
  \hline
  $\mathfrak{g}$ & Extended diagram of $\mathfrak{g}$ & Diagrams of the subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ \\
  \hline
  $A_n$ & \includegraphics{A_series_ext_diag.pdf} & \includegraphics{A_series_ext_split.pdf} \\
  \hline
  $B_n$ & \includegraphics{B_series_ext_diag.pdf} & \includegraphics{B_series_ext_split.pdf} \\
  \hline
  $C_n$ & \includegraphics{C_series_ext_diag.pdf} & \includegraphics{C_series_ext_split.pdf} \\
  \hline
  $D_n$ & \includegraphics{D_series_ext_diag.pdf} & \includegraphics{D_series_ext_split.pdf} \\
  \hline
\end{tabular}
\caption{Subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ for the classical series}}
\end{table}
If $\mathfrak{a}=B_{r_{\mathfrak{a}}}$  we see that $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\; 1<i<j\leq r-r_{\mathfrak{a}}\}$ and $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}}$. This is the only case where the simple roots of $\mathfrak{a}_{\bot}$ can not be obtained from the extended Dynkin diagram, as can be seen in the Table \ref{tab:diagrams}.

Using the existing classification of maximal special subalgebras in classical Lie algebras \cite{dynkin1952semisimple} we have the following pairs of the orthogonal subalgebras $\mathfrak{a},\;\mathfrak{a}_{\bot}$
\begin{equation}
  \label{eq:42}
  \begin{array}{lll}
      su(p)\oplus su(q) & \subset su(pq) &\\
      so(p)\oplus so(q) & \subset so(pq) &\\
      sp(2p)\oplus sp(2q) & \subset so(4pq)&\\
      sp(2p)\oplus so(q) & \subset sp(2pq)&\\
      so(p)\oplus so(q) & \subset so(p+q)& \text{for}\;p\;\text{and}\;q\;\text{odd}\\
  \end{array}
\end{equation}
Exceptional Lie algebras and other non-maximal subalgebras will be considered elsewhere.

@@

Using this property we can consider the restriction $ch\, L^{\mu}_{\mathfrak{g}\downarrow \mathfrak{a}_{\bot}\oplus \mathfrak{h}}$, that is the character of the direct sum of $\left( \mathfrak{a}_{\bot}\oplus\mathfrak{h}\right) $-modules.
Multiply the equation (\ref{eq:4}) by the element
\begin{equation}
  \label{eq:5}
  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)
\end{equation}
and take into account that the projection commutes with the multiplication:
\begin{multline}
  \label{eq:7}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}.
\end{multline}
Similarly to the transformation proposed in \cite{ilyin812pbc} we introduce the anomalous branching coefficients $k_{\lambda}$,
\begin{equation}
  \label{eq:10}
  \sum_{\nu \in P_{\frak{a}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
        a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\frak{a}}}k_{\lambda
  }^{\left( \mu \right) }e^{\lambda }
\end{equation}
and simplify the first factor,
\begin{multline}
  \label{eq:12}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
  \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta^{+}_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{a}}(\alpha)} \right)
    \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda }
\end{multline}

>>>>

\documentclass[12pt]{iopart}
\usepackage{ucs}
%\usepackage{amsmath,amssymb,amsthm}
\usepackage{iopams,amssymb,amsthm}
%\usepackage{pb-diagram}
\usepackage{multicol}
%\usepackage[utf8x]{inputenc}
%\usepackage[russian]{babel}
\usepackage{cmap}
\usepackage{color}
%\usepackage[pdftex]{graphicx}
\usepackage{graphicx}
%\pagestyle{plain}
%\usepackage[unicode,verbose,plainpages=false]{hyperref}
\usepackage{hyperref}

%\usepackage{verbatim} 
%\newenvironment{comment}
%{\par\noindent{\bf TODO}\\}
%{\\\hfill$\scriptstyle\blacksquare$\par}

\newtheorem{statement}{Statement}
\newtheorem{mynote}{Note}[section]
%\theoremstyle{definition} \newtheorem{Def}{Definition}
\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}

\begin{document}
% \pagenumbering{alph}
% \thispagestyle{empty}
% 
% \begin{center}
% {\Large \bf SAINT-PETERSBURG STATE\\[0.5cm] UNIVERSITY}
% \end{center}
% \vskip 1 cm
% \begin{flushright}
% {\large \bf SPbU-IP-10-03}
% \end{flushright}
% \hfill {}
% \vskip 1 cm
% \begin{center}
% {\Huge \bf Recursive algorithms, branching coefficients \\ and applications\\[0.5cm]
% }
% \end{center}
% \vskip 1.0 cm
% \begin{center}
% {\Large \bf
% Vladimir Lyakhovsky\\[2mm]
% Anton Nazarov}
% \end{center}
% \vfill
% \begin{center}
% {\large Department of Theoretical Physics\\
% }
% \end{center}
% \vfill
% \begin{center}
% SAINT-PETERSBURG \\
% 2010
% \end{center}
% 
% \newpage
% 
% \pagenumbering{arabic}
\title{Recursive algorithms, branching coefficients and applications}
\author{V D Lyakhovsky$^1$ and A A Nazarov$^2$} 
\address{$^{1,2}$ Theoretical Department, SPb State University,
198904, Sankt-Petersburg, Russia }
\eads{$^1$ \mailto{lyakh1507@nm.ru}, $^2$ \mailto{antonnaz@gmail.com}}
% \thanks{ Supported by
%  RFFI grant N 09-01-00504 and the National Project RNP.2.1.1./1575 }\\
% 
% \thanks{ Supported by
% the National Project RNP.2.1.1./1575 }

\begin{abstract}
  Recurrent relations for branching coefficients in affine Lie algebras integrable highest weight modules are studied. The decomposition algorithm based on the injection fan technique is adopted to the situation where the Weyl denominator becomes singular with respect to a reductive subalgebra. We study some modifications of the injection fan technique and demonstrate that it is possible to define the "subtracted fans" that play the role similar to the original ones. Possible applications of subtracted fans in CFT models are considered.
\end{abstract}
\submitto{\JPA}
%\maketitle

@@

$r$ , $\left( r_{\frak{a}}\right) $ --- the rank of the algebra $\frak{g}$ $%
\left( \mbox{resp. }\frak{a}\right) $ ;

$\Delta $ $\left( \Delta _{\frak{a}}\right) $--- the root system; $\Delta
^{+} $ $\left( \mbox{resp. }\Delta _{\frak{a}}^{+}\right) $--- the positive
root system (of $\frak{g}$ and $\frak{a}$ respectively);

@@

$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\frak{a}}^{\nu }\right) $ --- the
weight diagram of $L^{\mu }$ $\left( \mbox{resp. }L_{\frak{a}}^{\nu }\right)
$ ;

@@

$\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ --- the $i
$-th (resp. $j$-th) basic root for $\frak{g}$ $\left( \mbox{resp. }\frak{a}%
\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;

@@

$\alpha _{i}^{\vee }$ , $\left( \alpha _{\left( \frak{a}\right) j}^{\vee
}\right) $--- the basic coroot for $\frak{g}$ $\left( \mbox{resp. }\frak{a}%
\right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;

$\co{\xi }$ , $\co{\xi _{\left( \frak{a}\right) }}$
--- the finite (classical) part of the weight $\xi \in P$ , $\left( \mbox{%
resp. }\xi _{\left( \frak{a}\right) }\in P_{\frak{a}}\right) $;

@@

$P$ $\left( \mbox{resp. } P_{\frak{a}}\right) $ \ --- the weight lattice;

$M \left( \mbox{resp. }M_{\frak{a}}\right) :=$

\noindent $=\left\{
\begin{array}{c}
\sum_{i=1}^{r}\mathbf{Z}\alpha _{i}^{\vee }\mbox{ }\left( \mbox{resp. }%
\sum_{i=1}^{r}\mathbf{Z}\alpha _{\left( \frak{a}\right) i}^{\vee }\right)
\mbox{for untwisted algebras or }A_{2r}^{\left( 2\right) }, \\
\sum_{i=1}^{r}\mathbf{Z}\alpha _{i}\mbox{ }\left( \mbox{resp. }\sum_{i=1}^{r}%
\mathbf{Z}\alpha _{\left( \frak{a}\right) i}\right) \mbox{for }A_{r}^{\left(
u\geq 2\right) }\mbox{ and }A\neq A_{2r}^{\left( 2\right) },
\end{array}
\right\} ;$\\
$\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w\circ (\mu +\rho )-\rho }$ --- the singular weight element for the $\frak{g}$-module $L^{\mu }$;
$\Psi _{\left( \frak{a}\right) }^{\left( \nu \right) }:=\sum\limits_{w\in W_{\frak{a}}}\epsilon (w)e^{w\circ (\nu +\rho
_{_{\frak{a}}})-\rho _{_{\frak{a}}}}$ --- the corresponding singular weight
element for the $\frak{a}$-module $L_{\frak{a}}^{\nu }$;

$\widehat{\Psi ^{\left( \mu \right) }}$ $\left( \widehat{\Psi _{\left( \frak{%
a}\right) }^{\left( \nu \right) }}\right) $ --- the set of singular weights $%
\xi \in P$ $\left( \mbox{resp. }\in P_{\frak{a}}\right) $ for the module $%
L^{\mu }$ $\left( \mbox{resp. }L_{\frak{a}}^{\nu }\right) $ with the
coordinates $\left( \co{\xi },k,n,\epsilon \left( w\left( \xi
\right) \right) \right) \mid _{\xi =w\left( \xi \right) \circ (\mu +\rho
)-\rho },$ (resp. $\left( \co{\xi },k,n,\epsilon \left(
w_{a}\left( \xi \right) \right) \right) \mid _{\xi =w_{a}\left( \xi \right)
\circ (\nu +\rho _{a})-\rho _{a}}$ ),

$m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\xi }^{\left( \nu \right)
}\right) $ --- the multiplicity of the weight $\xi \in P$ \ $\left( \mbox{%
resp. }\in P_{\frak{a}}\right) $ in the module $L^{\mu }$ , (resp. $\xi \in
L_{\frak{a}}^{\nu } $);

$ch\left( L^{\mu }\right) $ $\left( \mbox{resp. }ch\left( L_{\frak{a}}^{\nu
}\right) \right) $--- the formal character of $L^{\mu }$ $\left( \mbox{resp. }%
L_{\frak{a}}^{\nu }\right) $;

@@

\noindent $\left( \mbox{resp. }R_{\frak{a}}:=\prod_{\alpha \in \Delta _{%
\frak{a}}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\frak{a}}\mathrm{%
\left( \alpha \right) }}=\Psi _{\frak{a}}^{\left( 0\right) }\right) $--- the
denominator.

@@

Our aim is to demonstrate that despite the zeros arriving in the Weyl denominator $R$
(when it is projected to the $P_{\mathfrak{a}}$) the injection fan technique \cite{ilyin812pbc} can be properly modified.
The result is the generalized recurrent relation for anomalous branching
coefficients \ref{eq:21}:
\begin{equation}
  \label{eq:1}
  \begin{array}{c}
      k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+ \right.\\
\left.
+\sum_{\gamma \in
\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
+\gamma }^{\left( \mu \right) }\right)
  \end{array}
   \end{equation}
Here $\mathfrak{a}_{\bot}$ is the subalgebra fixed by those roots of $\mathfrak{g}$ that are
orthogonal $P_{\mathfrak{a}}$, $W_{\bot}$ is the corresponding Weyl group,
$\Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ is the set of weights in the expansion
of the product $\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\mathfrak{a}_{\bot}}}
(1-e^{-\alpha})^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\alpha)}$ and $s(\gamma)$
is the multiplicity of $e^{\gamma}$ in this expansion.
In the next subsection we study the situation in details and prove the relation \ref{eq:1}.

@@

Such effects are due to the fact that the subalgebras $\mathfrak{a}$ and $\mathfrak{a}_{\bot}$ must not form a direct sum in $\mathfrak{g}$.  
Consider the case of such a regular embedding $\mathfrak{a}\subset \mathfrak{g}$ where both algebras are simple and the diagram of the subalgebra $\mathfrak{a}_{\bot}$ is not a subdiagram of the extended Dynkin diagram $\mathfrak{g}$.
 Drop the subdiagram of $\mathfrak{a}$ and the node $\alpha'$ that connects it with all the remaining nodes of the diagram of $\mathfrak{g}$. The remaining diagram is the diagram of the algebra $\mathfrak{\bar{a}}$ with $\mathrm{rank}(\mathfrak{\bar{a}}) = \mathrm{rank}(\mathfrak{g})-\mathrm{rank}(\mathfrak{a})$. It is clear that $\mathfrak{\bar{a}}\subset \mathfrak{a}_{\bot}$. So the question is whether $\mathfrak{a}_{\bot}$ has additional roots,  not the roots of $\mathfrak{\bar{a}}$ but the linear combinations of them. The answer is positive  when the set of angles between the roots of $\mathfrak{\bar{a}}$ does not contain all the angles between the roots of $\mathfrak{a}$. Then by reflecting the roots of $\mathfrak{a}$ by $s_{\alpha'}$ we get the additional roots of $\mathfrak{a}_{\bot}$. 
\begin{table}[ph]
\label{tab:diagrams}
\noindent  \centering{
\begin{tabular}{|l|l|l|l|}
  \hline
  $\mathfrak{g}$ & Extended diagram of $\mathfrak{g}$ & Diagrams of the subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ \\
  \hline
  $A_n$ & \includegraphics{A_series_ext_diag.eps} & \includegraphics{A_series_ext_split.eps} \\
  \hline
  $B_n$ & \includegraphics{B_series_ext_diag.eps} & \includegraphics{B_series_ext_split.eps} \\
  \hline
  $C_n$ & \includegraphics{C_series_ext_diag.eps} & \includegraphics{C_series_ext_split.eps} \\
  \hline
  $D_n$ & \includegraphics{D_series_ext_diag.eps} & \includegraphics{D_series_ext_split.eps} \\
  \hline
\end{tabular}
\caption{Subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ for the classical series}}
\end{table}
If $\mathfrak{a}=B_{r_{\mathfrak{a}}}$  we see that $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\; 1<i<j\leq r-r_{\mathfrak{a}}\}$ and $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}}$. This is the only case where the simple roots of $\mathfrak{a}_{\bot}$ can not be obtained from the extended Dynkin diagram, as can be seen in the Table \ref{tab:diagrams}.

Using the existing classification of maximal special subalgebras in classical Lie algebras \cite{dynkin1952semisimple} we have the following pairs of the orthogonal subalgebras $\mathfrak{a},\;\mathfrak{a}_{\bot}$
\begin{equation}
  \label{eq:42}
  \begin{array}{lll}
      su(p)\oplus su(q) & \subset su(pq) &\\
      so(p)\oplus so(q) & \subset so(pq) &\\
      sp(2p)\oplus sp(2q) & \subset so(4pq)&\\
      sp(2p)\oplus so(q) & \subset sp(2pq)&\\
      so(p)\oplus so(q) & \subset so(p+q)& \mbox{for}\;p\;\mbox{and}\;q\;\mbox{odd}\\
  \end{array}
\end{equation}
Exceptional Lie algebras and other non-maximal subalgebras will be considered elsewhere.

@@

Using this property we can consider the restriction $ch\, L^{\mu}_{\mathfrak{g}\downarrow \mathfrak{a}_{\bot}\oplus \mathfrak{h}}$, that is the character of the direct sum of $\left( \mathfrak{a}_{\bot}\oplus\mathfrak{h}\right) $-modules.
Multiply the equation (\ref{eq:4}) by the element
\begin{equation}
  \label{eq:5}
  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)
\end{equation}
and take into account that the projection commutes with the multiplication:
\begin{eqnarray*}
  \label{eq:7}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}.
\end{eqnarray*}
Similarly to the transformation proposed in \cite{ilyin812pbc} we introduce the anomalous branching coefficients $k_{\lambda}$,
\begin{equation}
  \label{eq:10}
  \sum_{\nu \in P_{\frak{a}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
        a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\frak{a}}}k_{\lambda
  }^{\left( \mu \right) }e^{\lambda }
\end{equation}
and simplify the first factor,
\begin{eqnarray*}
  \label{eq:12}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
  \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta^{+}_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{a}}(\alpha)} \right)
    \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda }
\end{eqnarray*}
